---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# rfishprod

<!-- badges: start -->
<!-- badges: end -->

Implements a framework to generate individual-level estimates
    of fish productivity, with a focus on reef fishes. This individual
    approach works by combining estimates of somatic growth through the
    von Bertalanffy Growth Model, and deterministic or stochastic natural
    mortality using instantaneous mortality rates.

## Installation

You can install rfishprod from [GitHub](https://github.com/renatomoraisaraujo/rfishprod) with:

``` r
devtools::install_github("renatomoraisaraujo/rfishprod")
```

## Example

Provide a simple reproducible example here:

```{r example}
library(rfishprod)
## basic example code
```

You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date.

In that case, don't forget to commit and push the resulting figure files, so they display on GitHub!
